The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-12-14 donde.tex
prepare for submission

 \documentclass[oneside,11pt]{article}

@@

\maketitle
\thispagestyle{empty}
\begin{abstract}

%Many firms provide commitment devices that restrict individuals' choice, but shroud this. Shrouding suggests low demand for commitment. We show that private paternalism is beneficial in the pawnbroker context we study.

We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending. Forcing borrowers into commitment contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% inclusive of fees, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%. Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the treated and the untreated simultaneously, along with the average selection on gains. We find large and significant effects of commitment even for borrowers who would not voluntarily choose it, and no evidence of selection on gains: borrowers who would freely choose commitment do not appear to benefit more than borrowers who would not. A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment. %The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.

@@

\vspace{.3in}

@@

\newpage

@@

\section{Introduction}

@@

We apply this approach to an important and understudied context: pawnshop lending. 
Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For purposes of comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{There is a large literature showing that stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (\url{https://tinyurl.com/yc2x5bjf}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent. The fee serves as a reminder and a means of reinforcing the importance of these interim payments. In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.

@@

Pawn loans involve individuals leaving valuable liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan. Collateral is typically more valuable than the loan amount, allowing lenders to give the loan immediately without checking a borrower's credit history. This makes pawn loans a popular way to get cash to pay for emergencies. In fact, they are one of the most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts. For comparison there were 2.3 million micro-finance clients across all lenders in Mexico in 2009 \citep{Pedroza:2010}.

@@

\paragraph{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash. No other collateral and no credit history checks are needed. The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e. a teller, see Figure \ref{PawnshopPicture}). The appraiser weighs the gold piece and runs tests on its purity. Based on these she assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client. The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.

\paragraph{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period. The client could make payments at the branch at any time with no penalty for pre-payment. Under this status quo contract, there are no payment reminders or any other kind of interim contact between the lender and the borrower. If the client returns to pay the principal plus the accumulated interest within 105 days, she recovers her pawn, otherwise the pawnbroker keeps the piece \textit{and} any payments already made. Before the contract expires, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and the same piece as the original contract (38\% of borrowers renew at least once with a given pawn). This contract is standard in the industry.  Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.

\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.  When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).

\paragraph{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:

@@

\vspace{.1in}

Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, stratified by whether we observed that they ended in default or recovery of the pawn. Figure \ref{fc_hist}(b) shows the analogous histogram for the APR.
%defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). 
We see that borrowers who default incur higher costs; part of this is mechanical as losing their collateral is part of the cost. Most of the APR costs indeed come from clients who do not recover their pawn.
%The second thing to note is that those that are not closed at the end of our sample period have already incurred substantial financial cost, even though they have not defaulted yet.

%Of those who renew, 83\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn. Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}

@@

\subsection{Treatment arms and randomization}

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.  It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, the same loan size/collateral ratio (70\%), and the same loan term (90 days, and a grace period of 15 days). Borrowers' gold pawns are appraised in the same way by the same appraisers under both the new and status quo contracts. The commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments. %\textcolor{red}{The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee.} 
The fee was modest and intended to make the payment deadlines salient. As a benchmark, the transportation cost to visit the branch to make a payment is comparable to the fee, on average.
%\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
%In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}

@@

%The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects. One may worry for instance that low sophistication from pawn-loans users could lead to the `wrong' people choosing the structured commitment contract. To examine this issue, we included an arm that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment. This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose. This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.

@@

\paragraph{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments. For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days. Figure \ref{exp_description} also illustrates the number branch-days per arm, the number of loans, and the number of surveys. %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them. There were two reasons: \hl{XXX}.

\paragraph{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms. To ensure this, we built two ``check-points'' as follows.  Two enumerators were present in each branch for the whole day during the duration of our experiment. At the first checking, these enumerators explained the contract terms to clients, emphasizing that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, along with the nature of the fees associated with the Commitment arm. Figure \ref{ExplanatoryMaterial} presents an excerpt of the materials we used to explain the contracts, translated into English. The explanation took about 3-5 minutes and continued until the client said she understood the contract terms. Enumerators then asked clients to explain the contract back to them before correcting any misunderstandings. At the second check-point the appraiser made clients read the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip} before they signed the contract. This summary was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract. The appraiser read it aloud and then asked the client to sign it as proof of understating. %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3). 
%Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms. The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.
%\footnote{That we can systematically predict demand based on consumer characteristics and measured beliefs suggest that take up is not random.}

@@

\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented. The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the item's value), the date of the pawn transaction, and the type of contract for that pawn: commitment or status quo. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013. This includes all the pawns that took place during our experiment along with those that one month before and eight months after our experiment. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 8,519 pawns while our administrative data covers a total of 26,180 pawns.

\paragraph{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day. The survey was intentionally short to avoid discouraging the potential clients from pawning. It measured demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time-consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 7,210 clients, and our survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
We only use the survey in Section \ref{Paternalism} of the paper.

@@

\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter the branch.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on individual borrowers.  Narrative reports and the way the treatment was implemented make us believe that selection into treatment is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.}

If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms. That is, if potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days. Table \ref{attrition_table} shows that this is not the case. There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day. Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability. The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece). Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms. The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns identical across arms.}

>>>>

\documentclass[11pt, a4paper]{article}

@@

\maketitle
\vspace{-0.75in}

\begin{abstract}
%Many firms provide commitment devices that restrict individuals' choice, but shroud this. Shrouding suggests low demand for commitment. We show that private paternalism is beneficial in the pawnbroker context we study.

\small {We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending. Forcing borrowers into commitment contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% inclusive of fees, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%. Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the choosers and the non-choosers simultaneously, along with the average selection on gains. We find large and significant effects of commitment even for borrowers who would not voluntarily choose it, and no evidence of selection on gains: borrowers who would freely choose commitment do not appear to benefit more than borrowers who would not. A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment.} %The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.

@@

@@

\vspace{3.75in}

@@

\newpage
\section{Introduction}

@@

We apply this approach to an important and understudied context: pawnshop lending. 
Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent. The fee serves as a reminder and a means of reinforcing the importance of these interim payments. In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.

@@

Pawn loans involve individuals leaving valuable liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan. Collateral is typically more valuable than the loan amount, allowing lenders to give the loan immediately without checking a borrower's credit history. This makes pawn loans a popular way to get cash to pay for emergencies. In fact, they are one of the most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion in yearly revenues.\footnote{See
\href{https://tinyurl.com/ybm56dpe}{here}, \href{https://tinyurl.com/y9zdcgws}{here}, and \href{https://tinyurl.com/y59ptdam}{here}.}
Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts. For comparison there were 2.3 million micro-finance clients across all lenders in Mexico in 2009 \citep{Pedroza:2010}.

@@

\vspace{.2in}
\noindent \textbf{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash. No other collateral and no credit history checks are needed. The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e. a teller, see Figure \ref{PawnshopPicture}). The appraiser weighs the gold piece and runs tests on its purity. Based on these she assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client. The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.

\vspace{.2in}
\noindent \textbf{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period. The client could make payments at the branch at any time with no penalty for pre-payment. Under this status quo contract, there are no payment reminders or any other kind of interim contact between the lender and the borrower. If the client returns to pay the principal plus the accumulated interest within 105 days, she recovers her pawn, otherwise the pawnbroker keeps the piece \textit{and} any payments already made. Before the contract expires, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and the same piece as the original contract (38\% of borrowers renew at least once with a given pawn). This contract is standard in the industry.  Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.

\vspace{.2in}
\noindent \textbf{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.  When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).

\vspace{.2in}
\noindent \textbf{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Figures \ref{fc_hist}(a) and \ref{fc_hist}(b)  in the appendix display histograms for financial cost and APR. Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:

@@

@@

\vspace{.2in}
\subsection{Treatment arms and randomization}

\vspace{.2in}
\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.  It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, the same loan size/collateral ratio (70\%), and the same loan term (90 days, and a grace period of 15 days). Borrowers' gold pawns are appraised in the same way by the same appraisers under both the new and status quo contracts. The commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments. %\textcolor{red}{The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee.} 
The fee was modest and intended to make the payment deadlines salient. As a benchmark, the transportation cost to visit the branch to make a payment is comparable to the fee, on average.
%\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
%In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}

@@

\begin{figure}[htbp]    
\begin{center}
\includegraphics[width=0.9\textwidth]{Figuras/consort.pdf}
  \end{center}
 \caption{Experiment description}
     \label{exp_description}
%\textit{Do file: }  \texttt{ss\_att.do}
\end{figure}

@@

\vspace{.2in}
\noindent \textbf{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments. For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days. Figure \ref{exp_description} also illustrates the number branch-days per arm, the number of loans, and the number of surveys. %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them. There were two reasons: \hl{XXX}.

\vspace{.2in}
\noindent \textbf{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms. To ensure this, we built two ``check-points'' as follows.  Two enumerators were present in each branch for the whole day during the duration of our experiment. At the first checking, these enumerators explained the contract terms to clients, emphasizing that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, along with the nature of the fees associated with the Commitment arm. Figure \ref{ExplanatoryMaterial} presents an excerpt of the materials we used to explain the contracts, translated into English. The explanation took about 3-5 minutes and continued until the client said she understood the contract terms. Enumerators then asked clients to explain the contract back to them before correcting any misunderstandings. At the second check-point the appraiser made clients read the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip} before they signed the contract. This summary was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract. The appraiser read it aloud and then asked the client to sign it as proof of understating. %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3). 
%Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms. The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.
%\footnote{That we can systematically predict demand based on consumer characteristics and measured beliefs suggest that take up is not random.}

@@

\vspace{.2in}
\noindent \textbf{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented. The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the item's value), the date of the pawn transaction, and the type of contract for that pawn: commitment or status quo. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013. This includes all the pawns that took place during our experiment along with those that one month before and eight months after our experiment. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 8,519 pawns while our administrative data covers a total of 26,180 pawns.

\vspace{.2in}
\noindent \textbf{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day. The survey was intentionally short to avoid discouraging the potential clients from pawning. It measured demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time-consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 7,210 clients, and our survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
We only use the survey in Section \ref{Paternalism} of the paper.

@@

\vspace{.2in}
\noindent \textbf{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter the branch.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on individual borrowers.  Narrative reports and the way the treatment was implemented make us believe that selection into treatment is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.}

If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms. That is, if potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days. Table \ref{attrition_table} shows that this is not the case. There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day. %Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability. The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece). Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms. The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}
%The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status. We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans. That is, the overwhelming marjority of potential borrowers did not leave the branch after learning which contract was on offer. Moreover, the extremely small fraction that did leave is balanced across arms.  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers. 
This is consistent with the findings of Table \ref{SS}.

\begin{table}[!h]
\caption{Summary statistics and Balance}
\label{SS}
\begin{center}
\resizebox{0.65\textwidth}{!}{
\scriptsize{\input{./Tables/SS.tex}}
}
\end{center}
\scriptsize {This table has two panels. Panel A uses administrative data at the loan level, while Panel B uses survey data. Each row in this table corresponds to a regression, where the level of observation is the individual loan originated. The dependent variables of these regressions are displayed in the first column. Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients. The admin data was a very limited set of pre-determined variables. The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend). The dependent variables in Panel B from the survey (see the questions in Table \ref{baseline_survey}. Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time. The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school. 
}
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

% To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day. The first row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=0.06), but we cannot reject equality with the Forced Commitment arm (p-value=0.41), or across all arms (p-value=0.16).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.  In no arm did more than three percent of individuals who responded to the survey go on to refuse loans, and neither these rates nor the rate of survey response are different across arms.  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.

% A less critical form of attrition is differential refusal to answer the survey questions.  The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.  Our core experimental estimates do not use the survey data as covariates, but the analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions. The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).
